% Sections
\newcommand{\bodyexperience}{EXPERIENCE}
\newcommand{\bodyeducation}{EDUCATION}
\newcommand{\bodycertificates}{CERTIFICATES}
\newcommand{\bodyprojects}{PROJECTS}
\newcommand{\bodyskills}{SKILLS}
\newcommand{\bodygreetings}{GREETINGS}
\newcommand{\bodymetadata}{
	General resume to be tailored by hand for each organization. If you receive this resume, something went wrong on my end!
}

% Contact
\newcommand{\bodyselfA}{Jesús Antonio González Quevedo}
\newcommand{\bodyselfB}{https://maps.app.goo.gl/U12Lxq6ALWDSuLdV9}
\newcommand{\bodyselfC}{Puebla, Puebla}
\newcommand{\bodyselfD}{tel:522222650774}
\newcommand{\bodyselfE}{+52 222 265 0774}
\newcommand{\bodyselfF}{mailto:jesugq@outlook.com}
\newcommand{\bodyselfG}{jesugq@outlook.com}
\newcommand{\bodyselfH}{https://www.linkedin.com/in/jesugq}
\newcommand{\bodyselfI}{jesugq}

% Experience
\newcommand{\bodycitibanamexA}{Banca Empresarial Citibanamex (Contractor)}
\newcommand{\bodycitibanamexB}{https://www.banamex.com}
\newcommand{\bodycitibanamexC}{faGlobe}
\newcommand{\bodycitibanamexD}{Dec 2021 — Feb 2025}
\newcommand{\bodycitibanamexE}{Associate QA Developer}
\newcommand{\bodycitibanamexF}{Java, Spring Boot, JDBC, Git, REST, SQL Developer, SQL Server, MongoDB, Karate}
\newcommand{\bodycitibanamexG}{Remote Work}
\newcommand{\bodycitibanamexH}{
	\item Supervised the release of 231 Java microservice updates (Mar 2024 - Feb 2025), supporting 32 development teams.
	\item Learned the business functions of 91 REST API microservices (Spring Boot, JDBC) across 5 environments and 6 gateways.
	\item Became knowledgeable in the communication between microservices and SQL/NoSQL databases, creating 61 query scripts.
	\item Analyzed 6 production incidents by tracing REST API requests and responses throughout encrypted productive logs.
	\item Increased test suite creation efficiency by 500\%, from 5 hours down to 1 for any given microservice.
	\item Trained a new hire for the role throughout 4 months whilst keeping up with deliverables.
	\item Kept up with deliverables for the duration of 6 months when the team shrunk down from 4 members to 1.
}
%
\newcommand{\bodymotivusA}{Motivus}
\newcommand{\bodymotivusB}{https://www.linkedin.com/company/motivustech}
\newcommand{\bodymotivusC}{faGlobe}
\newcommand{\bodymotivusD}{Aug 2021 — Present}
\newcommand{\bodymotivusE}{Associate Developer}
\newcommand{\bodymotivusF}{Java, Spring Boot, JDBC, JPA, Git, REST, SQL Developer, SQL Server, MongoDB, Karate}
\newcommand{\bodymotivusG}{Remote Work}
\newcommand{\bodymotivusH}{
	\item Led a team of 10 Java developers as a scrum master and backend developer, implementing a recruit assessment platform.
	\item Became the primary contributor to the Java (Spring Boot, JDBC, JPA) Git repository, pitching in 60\% of total lines of code.
	\item Got certified in two GCP roles, starting with a single exam voucher. Looking to get into AWS or Azure.
	\item Received access to Udemy courses (in use!) for consecutive years of high performance (Rating: 4 — Exceeds Expectations.)
	\item Joined a production incident team in Citibanamex via the contracting firm Motivus, formerly Anzen Soluciones.
}

% Education
\newcommand{\bodytecnologicomonterreyA}{Instituto Tecnológico de Estudios Superiores de Monterrey (ITESM PUE)}
\newcommand{\bodytecnologicomonterreyB}{https://certificados.tec.mx//dd14d13b16e750099a9783188f343e25}
\newcommand{\bodytecnologicomonterreyC}{faCheckCircle}
\newcommand{\bodytecnologicomonterreyD}{https://tec.mx/}
\newcommand{\bodytecnologicomonterreyE}{faGlobe}
\newcommand{\bodytecnologicomonterreyF}{Professional License in Computer Science and Technology Engineering}
\newcommand{\bodytecnologicomonterreyG}{Java, Git, C, Angular, Typescript, MySQL}

% Certificates
\newcommand{\bodyjavamasterclassA}{Java 17 Masterclass}
\newcommand{\bodyjavamasterclassB}{}
\newcommand{\bodyjavamasterclassC}{}
\newcommand{\bodyjavamasterclassD}{https://www.udemy.com/course/java-the-complete-java-developer-course/}
\newcommand{\bodyjavamasterclassE}{faGlobe}
\newcommand{\bodyjavamasterclassF}{offered by LP.Academy}
\newcommand{\bodyjavamasterclassG}{Java, Git, JShell}
\newcommand{\bodyjavamasterclassH}{}
%
\newcommand{\bodyclouddeveloperA}{Professional Cloud Developer}
\newcommand{\bodyclouddeveloperB}{https://www.credential.net/f05088e4-157e-40be-8d4f-b918be06f6c9}
\newcommand{\bodyclouddeveloperC}{faCheckCircle}
\newcommand{\bodyclouddeveloperD}{https://cloud.google.com/learn/certification/cloud-developer}
\newcommand{\bodyclouddeveloperE}{faGlobe}
\newcommand{\bodyclouddeveloperF}{certified by Google Cloud Platform}
\newcommand{\bodyclouddeveloperG}{GCP, Linux, Kubernetes}
\newcommand{\bodyclouddeveloperH}{Recertifying}
%
\newcommand{\bodycloudengineerA}{Associate Cloud Engineer}
\newcommand{\bodycloudengineerB}{https://www.credential.net/59c21655-2c0d-4803-ba06-3bad73fa3b69}
\newcommand{\bodycloudengineerC}{faCheckCircle}
\newcommand{\bodycloudengineerD}{https://cloud.google.com/learn/certification/cloud-engineer}
\newcommand{\bodycloudengineerE}{faGlobe}
\newcommand{\bodycloudengineerF}{certified by Google Cloud Platform}
\newcommand{\bodycloudengineerG}{GCP, Linux, Kubernetes}
\newcommand{\bodycloudengineerH}{Recertifying}
%
\newcommand{\bodyresponsivewebA}{Responsive Web Design}
\newcommand{\bodyresponsivewebB}{https://www.freecodecamp.org/certification/jesugq/responsive-web-design}
\newcommand{\bodyresponsivewebC}{faCheckCircle}
\newcommand{\bodyresponsivewebD}{https://www.freecodecamp.org/learn/2022/responsive-web-design/}
\newcommand{\bodyresponsivewebE}{faGlobe}
\newcommand{\bodyresponsivewebF}{certified by freeCodeCamp}
\newcommand{\bodyresponsivewebG}{HTML, CSS}
\newcommand{\bodyresponsivewebH}{}

% Skills
\newcommand{\bodydevelopmentA}{Development}
\newcommand{\bodydevelopmentB}{Java, Oracle Database, Javascript, Typescript, Git, C, Python, SQL, JUnit, Pytest, Gherkin}
\newcommand{\bodymethodologyA}{Methodology}
\newcommand{\bodymethodologyB}{Object-Oriented Programming, Web Development, Cloud Development, Native Spanish}
\newcommand{\bodymethodologyC}{Methodology}
\newcommand{\bodymethodologyD}{Version Control, IDE Debugging, Linux Terminal, Microservices, Databases}
\newcommand{\bodyenvironmentA}{Environment}
\newcommand{\bodyenvironmentB}{Google Cloud Platform, Linux, Github, IntelliJ, VSCode, TectiaSSH, Angular}
\newcommand{\bodyenvironmentC}{Environment}
\newcommand{\bodyenvironmentD}{LaTeX, SQL Server, MongoDB, SQL Developer, Jira, Confluence, Swagger, AsyncAPI, SoapUI, Postman, Karate}

% Projects
\newcommand{\bodyalgorithmsA}{Algorithms}
\newcommand{\bodyalgorithmsB}{}
\newcommand{\bodyalgorithmsC}{}
\newcommand{\bodyalgorithmsD}{https://github.com/jesugq/algorithms}
\newcommand{\bodyalgorithmsE}{faGithub}
\newcommand{\bodyalgorithmsF}{Java, Git}
\newcommand{\bodyalgorithmsG}{
	\item Currently solving algorithms found in LeetCode and the Java 17 Masterclass course.
	\item Applied code syntax suggestions from the course instructor and are currently learning coding best practices.
}
%
\newcommand{\bodyjavamasterfilesA}{Java 17 Masterclass}
\newcommand{\bodyjavamasterfilesB}{}
\newcommand{\bodyjavamasterfilesC}{}
\newcommand{\bodyjavamasterfilesD}{https://github.com/jesugq/jmc17}
\newcommand{\bodyjavamasterfilesE}{faGithub}
\newcommand{\bodyjavamasterfilesF}{Java, Git, JShell}
\newcommand{\bodyjavamasterfilesG}{
	\item Currently creating IntelliJ projects to study Java, Spring Boot as required by the Java 17 Masterclass course.
}
%
\newcommand{\bodylatexresumeA}{LaTeX Resume}
\newcommand{\bodylatexresumeB}{https://github.com/jesugq/resume/blob/master/resume.pdf}
\newcommand{\bodylatexresumeC}{faGlobe}
\newcommand{\bodylatexresumeD}{https://github.com/jesugq/resume}
\newcommand{\bodylatexresumeE}{faGithub}
\newcommand{\bodylatexresumeF}{Git, LaTeX}
\newcommand{\bodylatexresumeG}{
	\item Created a LaTeX resume with interactivity and language scalability in mind, supporting English \hypericon{https://github.com/jesugq/resume/blob/master/GONZALEZ_JESUS_EN.pdf}{faExternalLink} and Spanish \hypericon{https://github.com/jesugq/resume/blob/master/GONZALEZ_JESUS_ES.pdf}{faExternalLink}.
	\item Seamlessly changes between available languages without any loss in formatting or visible differences. All gray icons \hypericon{https://www.colorhexa.com/74729a}{faCircle} are clickable.
}
%
\newcommand{\bodygooglehomepageA}{Google Homepage}
\newcommand{\bodygooglehomepageB}{https://jesugq.github.io/google-homepage}
\newcommand{\bodygooglehomepageC}{faGlobe}
\newcommand{\bodygooglehomepageD}{https://github.com/jesugq/google-homepage}
\newcommand{\bodygooglehomepageE}{faGithub}
\newcommand{\bodygooglehomepageF}{Git, HTML, CSS, Flexbox}
\newcommand{\bodygooglehomepageG}{
	\item Recreated and customized the Google homepage from scratch without use of external libraries
	\item Further improved consistency between browsers using normalize css for web development.
}
%
\newcommand{\bodysudokusolverA}{Sudoku Solver}
\newcommand{\bodysudokusolverB}{}
\newcommand{\bodysudokusolverC}{}
\newcommand{\bodysudokusolverD}{https://github.com/jesugq/sudoku/tree/master/sudoku-cli}
\newcommand{\bodysudokusolverE}{faGithub}
\newcommand{\bodysudokusolverF}{Git, Python, Pytest}
\newcommand{\bodysudokusolverG}{
	\item Built a sudoku solving application using test-driven development in Python.
	\item Enhanced the algorithm to solve a medium difficulty puzzle in 1.4 seconds, down from 3.6 seconds.
}

% Cover
\newcommand{\bodycoverA}{
	To the Oracle team,
}
\newcommand{\bodycoverB}{
	Greetings! I came across your job opening on the Oracle Careers website. Oracle Java has always been my preferred programming language and I will forever thank you all for creating it, so I would love to be part of your group.
}
\newcommand{\bodycoverC}{
	After having worked with Java microservices for 4 years, I'd like to help the OAL Account Receivables team develop the Oracle Cloud Fusion Account Receivables standard product. I have studied the functionality of many, many Java microservices, and I think you'll be interested in my resume.
}
\newcommand{\bodycoverD}{
	Attached you will find my resume. I hope to hear from you soon	!
}
