% Sections
\newcommand{\langexperience}{EXPERIENCE}
\newcommand{\langeducation}{EDUCATION}
\newcommand{\langcertificates}{CERTIFICATES}
\newcommand{\langprojects}{PROJECTS}
\newcommand{\langskills}{SKILLS}
\newcommand{\langgreetings}{GREETINGS}
\newcommand{\langmetadata}{METADATA}

% Contact
\newcommand{\langpersonA}{Jesús Antonio González Quevedo}
\newcommand{\langpersonB}{https://maps.app.goo.gl/U12Lxq6ALWDSuLdV9}
\newcommand{\langpersonC}{Puebla, Puebla}
\newcommand{\langpersonD}{tel:522222650774}
\newcommand{\langpersonE}{+52 222 265 0774}
\newcommand{\langpersonF}{mailto:jesugq@yahoo.com}
\newcommand{\langpersonG}{jesugq@yahoo.com}
\newcommand{\langpersonH}{https://www.linkedin.com/in/jesugq}
\newcommand{\langpersonI}{jesugq}

% Cover
\newcommand{\langcoverA}{Greetings!}
\newcommand{\langcoverB}{Goodbye!}

% Experience
\newcommand{\langmotivusA}{Motivus}
\newcommand{\langmotivusB}{https://motivus.com/}
\newcommand{\langmotivusC}{faGlobe}
\newcommand{\langmotivusD}{Aug 2021 — Apr 2025}
\newcommand{\langmotivusE}{Associate Developer}
\newcommand{\langmotivusF}{Java, Google Cloud Platform, Spring Boot, JPA, IntelliJ, Git, Microservices}
\newcommand{\langmotivusG}{Remote Work}
\newcommand{\langmotivusH}{
	\item Led a team of 10 developers as both a Scrum Master and Java Developer, arranging our deliverables in Trello.
	\item Provided maintenance to a recruitment assessment platform hosted in Google Cloud Platform.
	\item Added the ability to query for users, groups, universities, and scores in the database using JPA.
	\item Became the primary contributor to the Java Git repository, pitching in 60\% of total new lines of code.
	\item Received a voucher for the Associate Cloud Engineer exam and got the certification (Even helping others get it!)
	\item Further deepened my Cloud Development skills by obtaining the Professional Cloud Developer certfications.
	\item Received access to Udemy courses (in use!) for consecutive years of high performance (Rating: 4 — Exceeds Expectations.)
	\item Joined a production incident team in Citibanamex via the contracting firm Motivus.
}
%
\newcommand{\langcitibanamexA}{Banca Empresarial Citibanamex (Contractor)}
\newcommand{\langcitibanamexB}{https://www.banamex.com}
\newcommand{\langcitibanamexC}{faGlobe}
\newcommand{\langcitibanamexD}{Dec 2021 — Feb 2025}
\newcommand{\langcitibanamexE}{Associate QA Developer}
\newcommand{\langcitibanamexF}{Java, Google Cloud Platform, Spring Boot, JDBC, IntelliJ, Git, Microservices}
\newcommand{\langcitibanamexG}{Remote Work}
\newcommand{\langcitibanamexH}{
	\item Supervised the release of 231 Java microservice updates by 32 development teams during the span of one year.
	\item Learned the functionality 91 Spring Boot microservices across 5 environments and 6 gateways.
	\item Verified the JDBC communication between microservices and their SQL/NoSQL databases using 61 query scripts.
	\item Analyzed 6 production incidents by tracing requests across microservices via their encrypted logs.
	\item Occasionally pair programmed to find the reasons behind the discrepancies in error formatting.
	\item Occasionally browsed through Git commits to find the line of code that reintegrated an already fixed bug. 
	\item Trained and mentored a new hire for the role throughout 4 months whilst keeping up with deliverables.
	\item Kept up with deliverables for the duration of 6 months when the team shrunk down from 4 members to 1.
	\item Further studied Java development with the Java 17 Masterclass udemy course.
	\item Further studied Cloud Development with both the Professional Cloud Developer and Associate Cloud Engineer certifications.
}

% Education
\newcommand{\langtecnologicomonterreyA}{Instituto Tecnológico de Estudios Superiores de Monterrey (ITESM PUE)}
\newcommand{\langtecnologicomonterreyB}{https://tec.mx/}
\newcommand{\langtecnologicomonterreyC}{faGlobe}
\newcommand{\langtecnologicomonterreyD}{https://certificados.tec.mx/certificate/dd14d13b16e750099a9783188f343e25}
\newcommand{\langtecnologicomonterreyE}{faCheckCircle}
\newcommand{\langtecnologicomonterreyF}{Professional License in Computer Science and Technology Engineering}
\newcommand{\langtecnologicomonterreyG}{Java, Google Cloud Platform, Git}
\newcommand{\langtecnologicomonterreyH}{
	\item Made use of Java by creating a contacts interface for the Object-Oriented Programming course.
	\item Made use of Java by creating a calendar interface for the Systems Design course.
	\item Made use of Google Cloud Platform by creating a login website using Google's Identity Provider.
	\item Stored said login's credentials in GraphQL hosted by Google's Firestore for the Web Applications Laboratory course.
	\item Made use of Google Cloud Platform by creating an online exam platform for the Web Applications Development course.
	\item Made use of Git in most programming projects (unlisted due to the use of other programming languages).
}

% Certificates
\newcommand{\langjavamasterclassA}{Learn Programming Academy}
\newcommand{\langjavamasterclassB}{https://www.udemy.com/course/java-the-complete-java-developer-course/}
\newcommand{\langjavamasterclassC}{faGlobe}
\newcommand{\langjavamasterclassD}{}
\newcommand{\langjavamasterclassE}{faCircleThin}
\newcommand{\langjavamasterclassF}{Java 17 Masterclass — 44\% done (232/522 lessons)}
\newcommand{\langjavamasterclassG}{Java, IntelliJ, Git, JShell}
\newcommand{\langjavamasterclassH}{
	\item Solved 49 algorithms in Java requiring principles such as Composition, Encapsulation, Polymorphism, Abstraction, Interfaces.
	\item Created 65 IntelliJ projects, applying principles such as Overloading, Inheritance, Factories, VarArgs, Generics, Nested Classes.
	\item Applied code syntax suggestions from the course instructor and are currently learning coding best practices.
}
%
\newcommand{\bodyclouddeveloperA}{Google Cloud Platform}
\newcommand{\bodyclouddeveloperB}{https://cloud.google.com/learn/certification/cloud-developer}
\newcommand{\bodyclouddeveloperC}{faGlobe}
\newcommand{\bodyclouddeveloperD}{https://www.credential.net/f05088e4-157e-40be-8d4f-b918be06f6c9}
\newcommand{\bodyclouddeveloperE}{faCheckCircle}
\newcommand{\bodyclouddeveloperF}{Professional Cloud Developer — 100\% done (384/384 lessons)}
\newcommand{\bodyclouddeveloperG}{Compute Engine, Kubernetes Engine, Cloud Functions, Cloud Build}
\newcommand{\bodyclouddeveloperH}{
	\item Deployed development environments and data storage in Compute Engine.
	\item Deployed user authentication and backend services in Compute Engine.
	\item Deployed a publisher / subscriber architecture using Cloud Functions.
	\item Deployed an application into Kubernetes Engine, automated by Cloud Build by listening to Source Repositories.
	\item Managed Scalability as well as Blue-Green and Canary deployments in Kubernetes Engine.
	\item See the full list of badges (the first half is related to this course) here. \hypericon{https://www.cloudskillsboost.google/public_profiles/f0976fc9-283a-49aa-b9a1-a214186ac3e4}{faExternalLink}
}
%
\newcommand{\bodycloudengineerA}{Google Cloud Platform}
\newcommand{\bodycloudengineerB}{https://cloud.google.com/learn/certification/cloud-engineer}
\newcommand{\bodycloudengineerC}{faGlobe}
\newcommand{\bodycloudengineerD}{https://www.credential.net/59c21655-2c0d-4803-ba06-3bad73fa3b69}
\newcommand{\bodycloudengineerE}{faCheckCircle}
\newcommand{\bodycloudengineerF}{Associate Cloud Engineer — 100\% done (306/306 lessons)}
\newcommand{\bodycloudengineerG}{App Engine, Cloud Run, Kubernetes Engine, Cloud Storage, BigQuery}
\newcommand{\bodycloudengineerH}{
	\item Explored Google Cloud Console's features; Marketplace, Networking, Virtual Machines, Load Balancing, Monitoring.
	\item Deployed Cloud Storage, Cloud SQL and BigQuery databases.
	\item Deployed containerized application images to App Engine, Cloud Run, Kubernetes Engine.
	\item Deployed a basic DevOps pipeline, automated by Cloud Build by listening to Source Repositories.
	\item See the full list of badges (the second half is related to this course) here. \hypericon{https://www.cloudskillsboost.google/public_profiles/f0976fc9-283a-49aa-b9a1-a214186ac3e4}{faExternalLink}
}